\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-23 paper/manuscript.tex
made most of the requested changes for the explanation of the random forest classifier

\subsection*{Boilerplate Classification}
In order to determine whether a line should be discarded, we train a classifier on a human-coded sample. We sampled 100 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA. To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type [@markus, please add an example here of a line that occurs a lot (e.g., "abc def" occurs in X documents in LA) to help the reader understand the concept of boilerplate lines happening frequently]. To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}

These 500 lines were then hand-coded as either substantively informative or not [@markus, how many were coded as boilerplate?]. We then trained a number of different classifiers with this informativeness measure as the dependent variable. The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself. The purpose of these covariates is as follows:

@@

We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assessed performance of this classifier through five-fold cross-validation [@markus, please add another sentence describing the five-fold CV], the results of which can be found in Table \ref{randomForest} [@markus, what package was used for this RF?]. [@markus, check that your writing is consistent with first-person plural] We use this classifier to flag and remove all lines that are not classified as substantively meaningful [@markus, how is the RF used to flag boilerplate lines (e.g., using a threshold of p = 0.5?]. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution looks more like what it should be [@markus, why is this what it "should be"]---lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). [@markus, this is an excellent demonstration of the effect of the classifier. When you get a chance, would you also add a table listing the top 10 most likely boilerplate lines---to provide face validity that we are accurately flagging boilerplate?] After all the preprocessing is set and done, our corpus consists of 259,099 documents.

>>>>

\subsection*{Boilerplate Classification}
In order to determine whether a line should be discarded, we train a classifier on a human-coded sample. We sampled 100 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA. To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type. As an example, the most common line throughout all pages of the city of Seattle consists only of the word ``total'' and occurs 103,068 times. Similarly, the line ``page'' occurs 58,833 times. Even something completely nonsensical such as ``a a'' still appears on 376 occasions. To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}

These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines). We then trained a number of different classifiers with this informativeness measure as the dependent variable. The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself. The purpose of these covariates is as follows:

@@

We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess performance of this classifier through five-fold cross-validation. This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score. This procedure is carried out five times, so that each sample is part of the test set once. The aggregated (mean) results of this process can be found in Table \ref{randomForest}. For the implementation of this method, we rely on the R package \texttt{caret}, whose random forest classifier is based on the package \texttt{ranger}. We use this classifier to flag and remove all lines that are not classified (based on a threshold of $p = 0.5$) as substantively meaningful. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution has changed---lines of medium length now occur more frequently than extremely short ones, which are unlikely to be substantively meaningful (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). [@markus, this is an excellent demonstration of the effect of the classifier. When you get a chance, would you also add a table listing the top 10 most likely boilerplate lines---to provide face validity that we are accurately flagging boilerplate?] After all the preprocessing is set and done, our corpus consists of 259,099 documents.
